Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression

### 2022-06-27 docs/rmd/presentation/slides.Rmd
kinda done

---
title: "Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression"
subtitle: "A comparison of epsilon-lexicase Selection and Tournament Selection"
author: "Roman Hoehn, B.Sc. Wirtschaftspaedagogik"
date: "2022-06-29"
output:
  beamer_presentation:
    theme: "Warsaw"
    fonttheme: "structurebold"
    keep_tex: true
    fig_caption: yes
    number_sections: true
    slide_level: 2
toc: yes
bibliography: ../bib/bib/ref.bib
csl: ../bib/csl/harvard1.csl
includes:
      in_header: header.tex
---

@@

\setbeamertemplate{footline}[frame number]

>>>>

---
title: "Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression"
subtitle: "A comparison of epsilon-lexicase Selection and Tournament Selection"
author: "Roman Hoehn"
institute: "JGU Mainz "
date: "2022-06-29"
output:
  beamer_presentation:
    theme: "Madrid"
    fonttheme: "structurebold"
    fig_width: 12
    fig_height: 10
    keep_tex: true
    fig_caption: yes
    number_sections: true
    slide_level: 2
toc: yes
bibliography: ../bib/bib/ref.bib
csl: ../bib/csl/harvard1.csl
includes:
      in_header: header.tex
---

@@

### 2022-06-27 docs/rmd/presentation/slides.tex
kinda done

@@

  pdfauthor={Roman Hoehn, B.Sc. Wirtschaftspaedagogik},

@@

\title{Analyzing the influence of Selection on Genetic Programming's
Generalization ability in Symbolic Regression}
\subtitle{A comparison of epsilon-lexicase Selection and Tournament
Selection}
\author{Roman Hoehn, B.Sc. Wirtschaftspaedagogik}
\date{2022-06-29}

@@

\begin{frame}[allowframebreaks]
  \tableofcontents[hideallsubsections]
\end{frame}
\begin{frame}
\setbeamertemplate{footline}{[}frame number{]}
\end{frame}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\begin{frame}{Related Concepts}
\protect\hypertarget{related-concepts}{}
\begin{block}{Symbolic Regression}
\protect\hypertarget{symbolic-regression}{}
\begin{itemize}
\tightlist
\item
  Task: Find a mathematical model that fits a given set of datapoints
\item
  One of the first applications of GP described by Koza (1992)
\item
  High relevance: GP can outperform state-of-the-art machine learning
  algorithms like gradient boosting \footnote<.->{Orzechowski, Cava and
    Moore (2018)}
\end{itemize}
\end{block}

\begin{block}{Generalization}
\protect\hypertarget{generalization}{}
\begin{itemize}
\tightlist
\item
  Main objective in most supervised machine learning problems: Achieve
  good performance for unseen data
\item
  Challenge: Avoid overfitting to training data
\item
  Little attention has been paid to generalization in GP \footnote<.->{O'Neill
    \emph{et al.} (2010), Kushchu (2002)}
\end{itemize}
\end{block}
\end{frame}

@@

\begin{frame}{Experiment}
\protect\hypertarget{experiment}{}
\begin{block}{Single run}
\protect\hypertarget{single-run}{}
\begin{itemize}
\tightlist
\item
  Total dataset (\(N=768\)) is randomly split into a training and
  testing dataset (50:50)
\item
  Fitness metric: Mean squared Error (MSE)
\item
  Train two models using GP with the training dataset only, one using
  tournament selection and the other \(\epsilon\)-lexicase selection
\item
  For each generation: Select elite model and compute its fitness for
  the testing dataset
\end{itemize}
\end{block}

>>>>

\usetheme[]{Madrid}

@@

  pdfauthor={Roman Hoehn},

@@

\title{Analyzing the influence of Selection on Genetic Programming's
Generalization ability in Symbolic Regression}
\subtitle{A comparison of epsilon-lexicase Selection and Tournament
Selection}
\author{Roman Hoehn}
\date{2022-06-29}
\institute{JGU Mainz}

@@

\begin{frame}[allowframebreaks]
  \tableofcontents[hideallsubsections]
\end{frame}
\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\begin{frame}{Related Concepts}
\protect\hypertarget{related-concepts}{}
\begin{block}{Symbolic Regression}
\protect\hypertarget{symbolic-regression}{}
\begin{itemize}
\tightlist
\item
  Task: Find a mathematical model that fits a given set of datapoints
\item
  One of the first applications of GP described by Koza (1992)
\item
  High relevance: GP can outperform state-of-the-art machine learning
  algorithms, e.g.~gradient boosting \footnote<.->{Orzechowski, Cava and
    Moore (2018)}
\end{itemize}
\end{block}

\begin{block}{Generalization}
\protect\hypertarget{generalization}{}
\begin{itemize}
\tightlist
\item
  Main objective in most supervised machine learning problems: Achieve
  good performance for unseen data
\item
  Challenge: Avoid overfitting to training dataset
\item
  Little attention has been paid to generalization in GP \footnote<.->{O'Neill
    \emph{et al.} (2010), Kushchu (2002)}
\end{itemize}
\end{block}
\end{frame}

@@

\begin{frame}{Experiment}
\protect\hypertarget{experiment}{}
\begin{block}{Single run}
\protect\hypertarget{single-run}{}
\begin{itemize}
\tightlist
\item
  Total dataset (\(N=768\)) is randomly split into a training/testing
  dataset (50/50)
\item
  Fitness metric: Mean squared Error (MSE)
\item
  Train two models using GP with the training dataset only, one using
  tournament selection and the other \(\epsilon\)-lexicase selection
\item
  For each generation: Select elite model and compute its fitness for
  the testing dataset
\end{itemize}
\end{block}
